Maps

### 2020-05-06 ms_8.Rmd
Final commit

@@

>>>>

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Number of Cows per Farm"

@@

```{r horses}
# Do horses have the same effect as cows??

# Prep data
horseData <- allData %>% mutate(horses_per_farm = horses/n_farm)

horseedu_model <- horseData %>%
  select(YEAR, pct_enrolled, horses_per_farm, avg_value_farm) %>%
  na.omit() %>%
  lm(pct_enrolled ~ horses_per_farm*avg_value_farm, data = .) %>%
  tidy(conf.int = TRUE)

horseedu_gt <- horseedu_model %>%
  select(term, conf.low, estimate, conf.high) %>%
  gt() %>%
  tab_header(title = "Effect Horses and Farm Value Enrollment",
             subtitle = "With 95% Confidence Interval") %>%
  cols_label(term = "Coefficient Name", conf.low = "Lower Bound", estimate = "Estimated Value", conf.high = "Upper Bound") %>%
  fmt_number(columns = vars(conf.low, estimate, conf.high), decimals = 4)

horseedu_gt

#gtsave(data = horseedu_gt, filename = "final/horseedu_gt.png")

# horse plot

horseedu_plot <- horseData %>%
  select(YEAR, pct_enrolled, horses_per_farm) %>%
  na.omit() %>%
  mutate(YEAR = as.factor(YEAR)) %>%
  group_by(YEAR) %>%
  ggplot(aes(x = horses_per_farm, y = pct_enrolled, color = YEAR)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_viridis_d() +
  ylim(0, 45) +
  scale_x_log10(labels = comma) +
  labs(title = "Horses and Education",
       subtitle = "Relationship between the number of horses per farm\nand school enrollment, by county",
       x = "Average Horses per Farm",
       y = "Percent of Population Enrolled in School") +
  theme_classic()

horseedu_plot
```
